6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
More footnotes

Reverse-engineering a system configuration is a non-trivial task. As this is not the primary intention of the tool, a simple approach is used to detect commonly installed services and provide some common default health checks for them. It relies upon standard UNIX commands such as `ps', `lsof' and `netstat' to detect running services.

@@

The streaming event service provides one endpoint to send all types of event data, this includes results from status checks, application performance metrics and log file entries. These types of event can all be processed and routed to a number of locations. This agnosticism makes it easy to adapt the monitoring architecture in future, hosts can be configured to send data to a single endpoint, which in turn can route the events to their appropriate location.

>>>>

Reverse-engineering a system configuration is a non-trivial task. As this is not the primary intention of the tool, a simple approach is used to detect commonly installed services and provide some common default health checks for them. It relies upon standard UNIX commands such as `ps'\footnote{ps - Retrieves the current process table}, `lsof'\footnote{lsof - Lists open 'file descriptors'} and `netstat'\footnote{netstat - Lists network status, including listening processes} to detect running services.

@@

The streaming event service provides one endpoint to send all types of event data, for example: results from status checks, application performance metrics and log file entries. These types of event can all be processed and routed to a number of locations. This agnosticism makes it easy to adapt the monitoring architecture in future, hosts can be configured to send data to a single endpoint, which in turn can route the events to their appropriate location.
